---
title: "AE 18: Sampling distributions & the Central Limit Theorem"
date: "October 25, 2021"
author: "STA 199"
---

# Learning goals 

- Recap simulation-based methods and `infer`
- Use Central Limit Theorem to define distribution of sample means
- Calculate probabilities from the normal distribution 

# Recap of simulation-based methods and `infer`

- Discussion of bootstrap, draw, and permute [here](https://infer.netlify.app/reference/generate.html).

  - Bootstrap: with replacement, for confidence intervals.
  
  - Draw: only for hypothesis testing for one proportion.
  
  - Permute: "shuffles" the data without replacement- see explanation[here](https://thomasleeper.com/Rcourse/Tutorials/permutationtests.html).

- Discussion of homework questions 2 & 4.

# Practice using CLT & Normal distribution

Suppose the bone density for 65-year-old women is normally 
distributed with mean $809 mg/cm^3$ and standard deviation of $140 mg/cm^3$.

Let $x$ be the bone density of 65-year-old women. We can write this distribution of $x$ in mathematical notation as 

$$x \sim N(809, 140)$$
# The Central Limit Theorem, Review

## The Central Limit Theorem

For a population with a well-defined mean $\mu$ and standard deviation
$\sigma$, these three properties hold for the distribution of sample
average $\bar{X}$,assuming certain conditions hold:

1.  The mean of the sampling distribution is identical to the population
    mean $\mu$,

2.  The standard deviation of the distribution of the sample averages is
    $\sigma/\sqrt{n}$, or the **standard error** (SE) of the mean, and

3.  For $n$ large enough (in the limit, as $n \to \infty$), the shape of
    the sampling distribution of means is approximately *normal* (Gaussian).

[**Check out this interactive
demonstration!**](http://onlinestatbook.com/stat_sim/sampling_dist/index.html)

## Exercise 1

What bone densities correspond to $Q_1$ (25th percentile), $Q_2$ (50th percentile), and $Q_3$ (the 75th percentile) of this distribution? Use the `qnorm()` function to calculate these values. 

```{r ex-1}

```

## Exercise 2

The densities of three woods are below:

- Plywood: 540 mg/cubic centimeter
- Pine: 600 mg/cubic centimeter
- Mahogany: 710 mg/cubic centimeter

- What is the probability that a randomly selected 65-year-old woman has bones less dense than Pine?

- Would you be surprised if a randomly selected 65-year-old  woman had bone density less than Mahogany? What if she had bone density less than Plywood? Use the respective probabilities to support your response. 

```{r ex-2}

```

## Exercise 3

Suppose you want to analyze the mean bone density for a group of 10 randomly selected 65-year-old women. 

- Are the conditions met use the Central Limit Theorem to define the distribution of $\bar{x}$, the mean density of 10 randomly selected 65-year-old women? 
  - Independence? 
  - Sample size/distribution? 
  
- What is the shape, center, and spread of the distribution of $\bar{x}$, the mean bone density for a group of 10 randomly selected 65-year-old women?

- Write the distribution of $\bar{x}$ using mathematical notation. 

## Exercise 4

- What is the probability that the mean bone density for the group of 10 randomly-selected 65-year-old women is less dense than Pine?

```{r ex-4-1}

```

- Would you be surprised if a group of 10 randomly-selected 65-year old women had a mean bone density less than Mahogany? What if the group had a mean bone density less than Plywood? Use the respective probabilities to support your response. 

```{r}

```

## Exercise 5

Please explain how your answers differ in Exercises 2 and 4.